Macro drop and droplet profile detection during PGMAW process by image processing

### 2011-01-26 articles/MIG/paper-drop_v1.tex
cb:maj Article MIG

A better observation of behavior of the weld pool or the metal droplet in a PGMAW process
 could help to  welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
 In a PGMAW process, the weld quality is strongly relates with the metal transfer  stability 
 (the droplet deposition). The monitoring of metal transfer process
 will indicate the good wire feed \cite{WANG}. 
The macro drop kinetic monitoring during static PGMAW process could help to better
understand some GMAW related phenomena  \cite{CHO} as free surface 
fluctuations \cite{WANG}. 
In both case, the kinetic and the dynamic analysis, required the monitoring \cite{} and the 
geometrical analysis of macro drop and droplets in order to extract 
qualitative information.

@@

There have been many studies on visual sensing techniques for observing weld pool 
image \cite{BAE} and metal transfer process during welding \cite{LIN}.
Optical sensors like high speed  cameras and lighting systems have been
widely use in GMAW process to realize  image acquisition \cite{ZHANG4},
control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}.
Image processing plays a critical role in extracting useful information from visual scenes \cite{WANG}.
Nevertheless the strong interference from the arc lightning required more than standard 
image treatment to analyses the raw images of the welding process \cite{NORDBRUCH}. 
Previous work has shown that is possible to perform geometrical 
analysis in weld pools or droplets \cite{WU1}.
Parameters such as macro drop or droplets surface, volumes 
or height has been measure using different and 
specific processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SEED},
\cite{NORDBRUCH}. However, to date, effectively automatic images processing
of metal transfer has not been developed, possibly due to the  difficulty involved 
for welding researchers \cite{WANG}.

To perform geometrical analysis in macro drope and droplet;
 a multipurpose C++ based library (erCv) was developed at the lab. 
These library results from selected functions  from highly reliable 
open source libraries to images treatment, geometrical 
analysis, graph theory applications and image visualization.
In a first step, and despite the different static and dynamic weld conditions, 
as well as different current regime. A reliable 2D profiles and geometrical
parameters from macro drop and droplets, has been obtained using the mentioned library.
 Using this, a dimension and dimensionless analysis will 
be done. The intention is to help to simplified futures numerical models of humping phenomena and quality process.

The paper is organized as follows. First, the purpose of the library is explained, then 
the experimental setup that will allow to appreciate the performance of the algorithm,
 to study macro drop analysis is detailed. The library and the algorithms
developed are explained and some results are shown on the macro drop and droplet study.

@@

The PGMAW static process is recorded by Shadowgraphy optical method. 
An halogen lamp is use to light the weld process. To guarantee an homogeneous
illumination of the welding process, a light diffuser is placed
in the optical path closer to the halogen lamp. 
Finally the shadows of welding elements are projected to the other side 
of the welding place. A Phantom V5.0 high speed camera is placed and aligned 
at the other of  the optical path (see figure \ref{schema-montage-experimental-GMAW}).

@@

To enhance the image contrast of the weld elements inside the electric discharge,
the intensity rate between arc light and halogen lamp have to be reduce. In order to this
a $650\ \pm 10\ nm$ band pass filter is place in front the camera lens. 650nm
is around emitting wavelength for the gases. Nevertheless, the raw images remain highly 
noisy by the arc light.

@@

Stationary spots weld are made using the GMAW process with the Oerlikon CitoWave 500 generator. 
The target is a steel disk of $10\ mm$ of thickness and 80mm radius.
The fill wire is ER70S steel welding of 1mm diameter.
The  wire feed speed is set to $6\ m/min$. The frequency droplets is set to $113\ Hz$. 
Two kind of  shielding gas were used \ref{tab::gases}. 
\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|}
\hline
Gaz & Argon (\%) & $CO_2$(\%) \\ \hline
G1 & 100       & 0 \\ \hline
G2 & 92        & 8 \\ \hline
\end{tabular}
\caption{Shielding gas composition}\label{tab::gases}
\end{table}

@@

Measurements are made using the erCv library.

@@

The purpose is to study the evolution of weld pool object in
a GMAW process or macro drop. Therefore it is necessary to study the shape and spreading
of the macro drop according depositing droplets of feed wire.

At figure \ref{schema-macro-drop-droplet-parameters} appears the geometrical 
elements to be study at the macro drop: the macro drop radius at the base $R_{m}$, 
the macro drop center height $h_{m}$, the macro drop volume $V_{m}$, the
penetration below the surface level $p$ and the wetting angles:
$\Theta_{m(al)}$, $\Theta_{m(ar)}$ (apparent) and $\Theta_{m(rl)}$, $\Theta_{m(rr)}$ (real).
With the indices $l$ and $r$ refer to left and
right angles. The indices: $m$ refer to macro drop, $g$ refer to gaz, $l$ refer
to liquid, $s$ refer to solid$/$substrate and $a$ refer to the droplet.

@@

Some definitions and brief description of generals principles used in
 image processing are required to better understand  the 
algorithms and the design of the library.

\subsection{Some definitions}\label{some_definitions}
A numerical grey image can be describe as 3D surface discretized by a grid mesh
 in the X,Y plane. Each mesh represents a pixel and the relief surface at Z axis,
 the grey level. 
A strong relief change or high gradient greyness values at
 the image are perceive by human eyes as light changes, and can be interpreted
 as objects edges.

@@

\subsection{Filters}\label{filters}

@@

\subsection{Snake and level set}
\label{snake-and-level-set}

@@

\subsection{Segmentation}
\label{segmentation}

@@

As mentioned, a multipurpose image processing library was developed 
and currently use at the laboratory, in order to analyze welding process objects.
erCv is able to perform edge detection and geometrical analysis in a different 
welding objects such: Macro drop, droplets and weld pool.
erCv is a modular library assembled in a oriented object C++ language. Then erCv is a scalable 
and portable library able to perform real time
 contour detection. erCv is implemented in  C++ with some bindings in python,
 making it relatively convivial to use.
erCv is compose by four processing modules based in C,  C++ and python language (see figure \ref{schema-erCv}). These modules are: 
\begin{description}
\item[Image Treatment:] Due to weld process conditions such arc lightening, 
 heat and electrodes positions; the raw image registered by CCD 
 camera are not calibrated and present light inhomogeneities and 
 noise. In order to obtain the real shape and size of weld elements, this module 
 include calibrations algorithms. To detect the welding objects contours it is 
 necessary to improve the weld element image. This module has the 
 pre-processing treatments to noise reduction and image enhancement.
 Then to start the edges detection process, this module includes processing
 algorithms as segmentations by samples comparators, watershed transformation,
 filters edge detectors and histogram based methods.  
\item[Geometrical Treatment and Analysis:] This module convert edges pixels points into connected 
   segments to end the edge detection
  process, completing and in some cases extrapolating the weld
  elements edge. It is also responsible to compute the geometrical 
  data of welding elements such weld pool surface and metal transfer drop volumes. 
  This module uses a full geometry algorithm library\cite{CGAL}, which include different algorithms
  such as triangulations and mesh generation, alpha shape and 
  convex hull generation and polygonal structures.
\item[Graph Theories:] To compute the geometrical data of welding elements
   it is necessary to extract the welding object edge from the image; this
   required some criteria such as continuity, length or closer condition.
   This module use graph algorithms to  identify and select the welding element edge using the
   criteria. This module is composed by connected segments, estimates
   minimal cut, determine largest chain segments and others algorithms. 
\item[Visualization:] This module is a set of 
  functions use to execute, show and/or register the 
  different steps at the image process.
\end{description}

\begin{figure}
\begin{center}
\includegraphics[width=7cm,height=4cm]{images/schema-erCv.png}
\caption{{\small Flow diagram of erCv library composition}}
\label{schema-erCv}
\end{center}
\end{figure}

@@

As was shown in section \ref{image-acquisition-setup}, the camera recording a 
shadow projection of the welding process. The projection is 
supposed to be a section of the welding process image, orthogonal to the optical path.
Therefore, to a first approach, not image projection 
correction is necessary. Only to calibrate the image dimension 
(at pixels) to the real objects dimension (at millimeters), a conversion scale is 
made with the known width of the welding wire $conv = 1\ mm/ 20\ pixels$ .

@@

However objects within the arc may differ only by few intensity light level
from the background. In these images areas a contrast enhancement is necessary. 
Objects outside the arc, as the some regions of the macro drop profile,
 are clearly visible against the background. In these regions a contrast enhancement 
can lead the image quality and thus an incorrect segmentation \cite{NORDBRUCH}.
 Therefore the contrast enhancements, or threshold, have to be adapted par regions in the image.

To simplify the contrast enhancement, the images are converted from RGB image color 
to grey levels image (see figure \ref{photo-macro-drop-grey}). To 
reduce the grey level noise, a first smooth classical filter 
(Blur) is applied over the image. The filter replace
the grey values of squares of $7\times 7$ 
pixels by they average value (see figure \ref{photo-macro-drop-smoothblur}). 
In consequence, the homogeneity quality is improve into the light and 
shadows regions, despite the edge contrast reduction induce between these regions.

Then, a regions adaptive threshold can be used to enhance the difference
between shadow elements and light zones. To the adaptive threshold it is important 
to choose the correct size region where it will be applied. Small regions to threshold
will generate isolates patters (groups of pixels). Big regions will generate
a classical like threshold image \cite{SABER}. The region size dominium choose
to threshold application is $23\times 23\ pixels$. The threshold criteria 
choose is binary: $greyL_{thres}(x,y) = max_{value}$ if $greyL_{origin}(x,y) >  threshold(x,y)$
or $greyL_{thres}(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter,
 $max_value$ is the grey level value choose to identify the pixels above
threshold parameter, $greyL_{origin}(x,y)$ is the grey level value of pixel
 before threshold and $greyL_{thres}(x,y)$ is the pixel grey level after threshold.
$threshold(x,y)$ is obtain by subtraction between the average grey level of region
 pixels neighborhood and a constant parameter $C_{threshold}$.  
Small edge defects can still be found, due to the previous smooth filter and some arc 
light interference regions, which are bigger than regions size to
threshold (see figure \ref{photo-macro-drop-adaptivethreshold}).

@@

Give $S$ the set of points in the space image. The segments could 
be building between wherever two points of $S$. However, to fulfill
 the cords with segments, only the points placed together could define
 a segment. To choose the correct points of $S$ a Delaunay triangulation
 is made over $S$ \cite{CGAL}. Each point of $S$ is a vertices 
of a triangle and then each potential segment is a side of a triangle. 
The Delaunay triangulations guarantee a unique solution with minimal internal angles for each triangle, which means  minimal length sides to the triangles \cite{GEOMETRICAL}.
 Give $\beta$ the cord surrounding the external hull of the Delaunay
 triangulation of $S$. An alpha shape algorithm uses a $\alpha \in N$ parameter,
 or square radius of a test circle, to travel from outside $\beta$ to inside
 the triangulation. The circle has to go through the triangles sides without touch the vertices. Give 
$n$ the number of triangles sides of triangulation
and $l_{i}$ with $i\in\{1,n\}$ the length of each side, if $\sqrt{\alpha} > l_{i}$ 
with $i \in\{1,n\}$, a segment is build between the respective vertices or
 points. At the end of the process, a segments set know as $\alpha$-shape has been created.  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape
 is $\beta$ \cite{CGAL}. If $\sqrt{\alpha} < l_{i} \forall i$ the circle go through
 every side in the triangulation,  then no segment are created and $\alpha$-shape
 became $S$. The points that compound the droplet section are all contact neighbors. Then $\alpha = 1$
 is sufficient to create a segment set around the droplet
 (see figure \ref{photo-droplet-alpha-shape}).

\begin{figure}[h!]
\begin{center}    
\subfigure[t = ]{\label{photo-droplet-canny}\includegraphics[width=3.5cm,height=3.5cm]{photo-droplet-canny.png}}
\subfigure[t = ]{\label{photo-droplet-alpha-shape}\includegraphics[width=3.5cm,height=3.5cm]{photo-droplet-alpha-shape.png}}\\
\end{center}
\caption{{\small Images series of macro drop profiles}}
\label{photo-results-droplet}
\end{figure}

@@

Now it is possible to determine the geometrical parameters shown 
at figure \ref{schema-macro-drop-droplet-parameters}. To compute the wetting 
angle measures, linear regressions or least squares (parabolic, ellipse, circle) 
are taken from the processed macro drop extracted profiles.
A loop algorithm applies this method to all frames at the experience to compute the wetting 
angles. Same procedure is use to estimate the macro drop radius and volume \cite{CHAPUIS}.

\section{ Results}
In this part some results, performance and reliability of the library for a set of experiment
are shown. The basic experiment is a static Pulsed Gas Tungsten Arc Welding.
A macrodrop is feed by droplets that are assumed to flight vertically and
then  feed the macro drop generated. The macrodrop grows with a geometry that depends on the effects of gravity,
surface tension, heat transfert,...

To improve weld quality in pulsed GMAW, the dynamic of the droplet is investigated.
The analysis focus on the regularity of the transfert and some statistics are shown.

@@

\begin{itemize}
\item The angle between the substrate and the liquid
\item The speed of growth of the macro drop radius
\end{itemize}

The first item give information on the capillarity mechanism involved in the macrodrop and
the second is an indicator of the ease of growth of the macrodrop due to
heat transfert and tension surface.

The shielding gas has a great effect between the liquid and the gas interface. Gas could diffuse in the
first layer of the liquid and greatly modify the physical properties. The tension surface is the main physical
property that will be modified. A difference of tension surface will modify the shape of the interface by modifying
its equilibrium. It has to be kept in mind that modification of shielding composition will also modify
the plasma energetical and momentum distribution that could also  influence the shape of the interface.

 To study the influence of the gases on the shape of the gas liquid interface, images must be selected in cold
regime of the plasma in the period. It is better to select images at the end of the period when the macrodrop is
stabilized. Once the images are selected, the algorithm described in section \ref{image_treatment} is used.
The treatment of each image last around 5ms.
\subsubsection{Basis and angle evolution} 
Some profile detection are shown on figure \ref{fig::photo-results-macro-drop} on the macrodrop.
The shape is shown on figure \ref{fig::photo-results-macro-drop}.

Angle and Radius could be measured with the contour. The workpiece surface is detected on the contour so 
that the macrodrop could be isolated. The developped algorithm manage to detect profile under the arc.
The algorithm to extract the macrodrop profile is  a thershold relative to the base material or workpiece.
The result is shown on figure \ref{fig:profile_extract}. Then, calculation of evolution on the profile can pe performed
all along  the process.
\begin{figure}[h!]
\centering    
\includegraphics[width=10cm]{images/CO2_2s.png}
\caption{Profile of macro drop for G1 gas after 2s of welding}
\label{fig::profile_extract}
\end{figure}
First, the evolution of the basis is extracted on figure \ref{fig::basis} by finding 
the min of the max of the contour on figure \ref{fig::profile_extract}.

@@

Another important geometrical entity is angle. To approximate it, a simple linear regression is
performed for the first and last points of the profile. The result are shown on figure \ref{fig::angles}
for the left angle and the two gases.
\begin{figure}[h!]
\centering    
\includegraphics[width=7cm,angle=90]{images/Evolution_Angle_Gazs.pdf}
\caption{Macrodrop left Angle in function of welding time}
\label{fig::angles}
\end{figure}

The evolution curves are noisy. Videos investigation show that the macrodrop oscillates during welding. 
Macrodrop oscillations induced left wetting angle oscillations. Depending of the main oscillations during
a period, the local angle oscillation is more or less important. For pure Argon
gas, the equilibrium angle (60 degrees) rapidly reached and stays constant all along the welding.
For the 8 per cent $CO_2$ gas, the angle increase until reaching a constant value of 60 degrees.

\subsubsection{Discussion}
The noise in the measure for the basis could be attributed
to oscillations of the macrodrop coupled to the threshold for the detection of the macrodrop.
The interface between the gas and liquid is extremely strained. During a pulse, the surface is perturbated by the
increase of pressure in the arc due to increase of current and by the impingement of the droplet inside the
weld pool. These phenomenon near the triple joint are transient. The growth of the macrodrop is a balance mainly between
the energy balance, the mechanical equilibrium (DuprÈ's law and membrane equilibrium). 
The energy balance is coupled to fluid flow in the weld pool. 
The shape of the macrodrop is an important information for
the mechanical equilibrium of the interface and to have information of mechanical acting on it.
For example, the macrodrop made with  pure Argon grows by step denoting an interesting instability 
of the interface.

The modification of gas influences surface tension but also modifies the energy transfert from the plasma
to the workpiece. Even with same welding parameters, 
the difference of gas will modify the current lines distribution but also the arc length.
Nevertheless, the evolution of the basis for the two gases are almost the same (figure \ref{fig::macrodrop}) as well
almost the same overall shape (figure \ref{fig::comp_gazs}). This means that at first order the two evolution
are governed with the same mechanism (mass balance) and then the difference is due to heat transfert and surface tension.

@@

\subsection{ Droplet flight}
Droplet flight investigation is of interest for weld quality and the metal deposition process.
The determination of the motion and the impact point is then a good indicator of the quality of the
process. The droplet flight is only investigated for the 8 per cent $CO_2$ for a pulse of 113 Hertz.
The treatment of each image takes between 5 to 45ms with geometrical algorithm (triangulation) and output
(surface computation and position of the center of mass).

@@

The position of the center of mass of the droplet relative to the vertical axis shows that the 
droplet has a constant speed. The speed is estimated between 150mm/s to 200mm/s depending on the pulse.

>>>>

A better observation of behavior of the weld pool or the metal droplet in a Pulsed Gas Metal Arx Welding (PGMAW)
 process could help to enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
 In a PGMAW process, the weld quality is strongly related with the metal transfer  stability 
 (droplet deposition). The monitoring of metal transfer process
 will indicate the good deposition process \cite{WANG}. 
The macro drop kinetic measurement during static PGMAW process could improve the
understanding of some GMAW related phenomenon  \cite{CHO} as free surface 
fluctuations \cite{WANG}. The measurement of the geometry of the free surface 
of macrodrop or droplets is an important information for the understanding and
the validation of the simulation.

@@

There have been many studies on visual sensing techniques for observing weld pool 
image \cite{BAE} and metal transfer process during welding \cite{LIN}.
Optical sensors like high speed  cameras and lighting systems have been
widely use in GMAW process to realize  image acquisition \cite{ZHANG4},
control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}.
Image processing plays a critical role in extracting useful information from visual scenes \cite{WANG}.
Nevertheless the strong interference from the arc lightning required more than standard 
image treatment to analyses the raw images of the welding process \cite{NORDBRUCH}. 
Previous work has shown that is possible to perform geometrical 
analysis in weld pools or droplets \cite{WU1}.
Parameters such as macro drop or droplets surface, volumes 
or height has been measured using different and 
specific processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SEED},
\cite{NORDBRUCH}. However, to date, effective automatic image processing
of metal transfer has not been developed, possibly due to the  difficulty involved 
for welding researchers \cite{WANG}.

To perform geometrical analysis in macrodrop and droplet,
 a multipurpose C++  library (erCv) was developed at the lab. 
These library results from selected functions  from highly reliable 
open source libraries to images treatment, geometrical 
analysis, graph theory applications and image visualization.
In a first step, and despite the different static and dynamic weld conditions, 
as well as different current regime. A reliable 2D profiles and geometrical
parameters from macro drop and droplets, has been obtained using the mentioned library.
 Using this, a dimension and dimensionless analysis will 
be done. The intention is to help to simplify future numerical models and enhance monitoring by direct observation.

The paper is organized as follows. First, the experimental setup that will allow to appreciate the performance of the algorithm,
 to study macro drop analysis is detailed in order to appreciate the difficulies of profile detection
during welding process. Then 
 The library and the algorithms are explained and some results are shown on the macro drop and droplet study.

@@

The PGMAW static process is recorded by Shadowgraphy optical method. 
An halogen lamp is used to light the weld process. To guarantee an homogeneous
illumination of the welding process, a light diffuser is placed
in the optical path closer to the halogen lamp. 
Finally the shadows of welding elements are projected to the other side where
 a Phantom V5.0 high speed camera is placed and aligned in
 the optical path (see figure \ref{schema-montage-experimental-GMAW}).

@@

To enhance the image contrast of the weld elements inside the electric discharge,
the intensity rate between arc light and halogen lamp have to be reduced. In order to this
a $650\ \pm 10\ nm$ band pass filter is placed in front the camera lens. 650nm
is around a no emitting wavelength from the arc. Nevertheless, the raw images remain highly 
noisy by the arc light.

@@

Stationary spots weld are made using the GMAW process with the Oerlikon CitoWave 500 generator. 
The target is a steel disk of $10\ mm$ of thickness and 80mm radius.
The fill wire is ER70S steel welding of 1mm diameter.
The  wire feed speed is set to $6\ m/min$. The frequency droplets is set to $113\ Hz$. 
Two kind of  shielding gases were used \ref{tab::gases}. 
\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|}
\hline
Gaz & Argon (\%) & $CO_2$(\%) \\ \hline
G1 & 100       & 0 \\ \hline
G2 & 92        & 8 \\ \hline
\end{tabular}
\caption{Shielding gas composition}\label{tab::gases}
\end{table}

@@

%Measurements are made using the erCv library.

@@

%The purpose is to study the evolution of weld pool object in
%a GMAW process or macro drop. Therefore it is necessary to study the shape and spreading
%of the macro drop according depositing droplets of feed wire.

At figure \ref{schema-macro-drop-droplet-parameters} appears the geometrical 
elements to be study at the macro drop: the macro drop radius at the base $R_{m}$, 
the macro drop center height $h_{m}$, the macro drop volume $V_{m}$, the
penetration below the surface level $p$ and the wetting angles:
$\Theta_{m(al)}$, $\Theta_{m(ar)}$ (apparent) and $\Theta_{m(rl)}$, $\Theta_{m(rr)}$ (real).
With the indices $l$ and $r$ refer to left and
right angles. The indices: $m$ refer to macro drop, $g$ refer to gaz, $l$ refer
to liquid, $s$ refer to solid$/$substrate and $a$ refer to the droplet.
The angles and the base are the two main quantities to be measured. but the overall shape of
the macrodrop is an important information for computation.

@@

Some definitions and brief description of general principles used in
 image processing are required to measure the profiles. Then, the design of the library is briefly detailed
to succeed to detect the profile in the noisy environment.
\subsection{Image treatment basics}
\subsubsection{Some definitions}\label{some_definitions}
A numerical grey image can be describe as 3D surface discretized by a grid mesh
 in the X,Y plane. Each mesh represents a pixel and the relief surface at Z axis,
 the grey level. 
A strong relief change or high gradient greyness values at
 the image are perceive by human eyes as light changes, and can be interpreted
 as objects edges.

@@

\subsubsection{Filters}\label{filters}

@@

\subsubsection{Snake and level set}
\label{snake-and-level-set}

@@

\subsubsection{Segmentation}
\label{segmentation}

@@

As mentioned, a multipurpose image processing library was developed 
and currently use at the laboratory, in order to analyze welding process objects.
erCv is able to perform edge detection and geometrical analysis in a different 
welding objects such: Macro drop, droplets and weld pool.
erCv is a modular library assembled in a oriented object C++ language. Then erCv is a scalable 
and portable library able to perform real time
 contour detection. erCv is implemented in  C++ with some bindings in python,
 making it relatively convivial to use for non-programmers.
erCv is composed by four processing modules: 
\begin{description}
\item[Image Treatment:] Due to weld process conditions such arc lightening, 
 heat and electrodes positions; the raw image registered by CCD 
 camera are not calibrated and present light inhomogeneities and 
 noise. In order to obtain the real shape and size of weld elements, this module 
 includes calibration algorithms. To detect the welding objects contours it is 
 necessary to improve the weld element image. This module has the 
 pre-processing treatments to noise reduction and image enhancement.
 Then to start the edges detection process, this module includes processing
 algorithms as segmentations by samples comparators, watershed transformation,
 filters edge detectors and histogram based methods.  
\item[Geometrical Treatment and Analysis:] This module convert edges pixels points into connected 
   segments to conclude the edge detection
  process, completing and in some cases extrapolating the weld
  elements edge. It is also responsible to compute the geometrical 
  data of welding elements such weld pool surface and metal transfer drop volumes. 
  This module uses a full geometry algorithm library\cite{CGAL}, which include different algorithms
  such as triangulations and mesh generation, alpha shape and 
  convex hull generation and polygonal structures.
\item[Graph Theories:] To compute the geometrical data of welding elements
   it is necessary to extract the welding object edge from the image; this
   required some criteria such as continuity, length or closer condition.
   This module use graph algorithms to  identify and select the welding element edge using the
   criteria. This module is composed by connected segments, estimates
   minimal cut, determine largest chain segments and others algorithms. 
\item[Visualization:] This module is a set of 
  functions use to execute, show and/or register the 
  different steps at the image process.
\end{description}

\begin{figure}
\begin{center}
\includegraphics[width=10cm]{images/schema-erCv.png}
\caption{{\small Flow diagram of erCv library composition}}
\label{schema-erCv}
\end{center}
\end{figure}

The originality of the library comes from the agregation and complementarity of the different numerical tools.
The main difficulty is to find algorithms with good parameters all along the process.

@@

As was shown in section \ref{image-acquisition-setup}, the camera recording a 
shadow projection of the welding process. The projection is 
supposed to be a section of the welding process image, orthogonal to the optical path.
Therefore, to a first approach, not image projection 
correction is necessary. Only to calibrate the image dimension 
(at pixels) to the real objects dimension (at millimeters), a conversion scale is 
made. In our experiment, the known width of the welding wire leads to $conv = 1\ mm/ 20\ pixels$ .

@@

However objects within the image under the arc may differ only by few intensity light level
from the background. In these images areas a contrast enhancement is necessary. 
Objects outside the arc, as the some regions of the macro drop profile,
 are clearly visible against the background. In these regions a contrast enhancement 
can lead the image quality and thus an incorrect segmentation \cite{NORDBRUCH}.
 Therefore the contrast enhancements, or threshold, have to be adapted par regions in the image.

To simplify the contrast enhancement, the images are converted from RGB image color 
to grey levels image (see figure \ref{photo-macro-drop-grey}). To 
reduce the grey level noise, a first smooth classical filter 
(Blur) is applied over the image. The filter replace
the grey values of squares of $7\times 7$ 
pixels by they average value (see figure \ref{photo-macro-drop-smoothblur}). 
In consequence, the homogeneity quality is improved into the light and 
shadows regions, despite the edge contrast reduction induce between these regions.

Then, a regions adaptive threshold can be used to enhance the difference
between shadow elements and light zones. To the adaptive threshold it is important 
to choose the correct size region where it will be applied. Small regions to threshold
will generate isolates patters (groups of pixels). Big regions will generate
a classical like threshold image \cite{SABER}. The region size dominium choose
to threshold application is $23\times 23\ pixels$. The threshold criteria 
choose is binary: $greyL_{thres}(x,y) = max_{value}$ if $greyL_{origin}(x,y) >  threshold(x,y)$
or $greyL_{thres}(x,y) = 0$ otherwise, $\forall (x,y)$ inside the region
to threshold \cite{OPENCV}. Where $threshold(x,y)$ is the threshold parameter,
 $max(value)$ is the grey level value choose to identify the pixels above
threshold parameter, $greyL_{origin}(x,y)$ is the grey level value of pixel
 before threshold and $greyL_{thres}(x,y)$ is the pixel grey level after threshold.
$threshold(x,y)$ is obtain by subtraction between the average grey level of region
 pixels neighborhood and a constant parameter $C_{threshold}$.  
Small edge defects can still be found, due to the previous smooth filter and some arc 
light interference regions, which are bigger than regions size to
threshold (see figure \ref{photo-macro-drop-adaptivethreshold}).

@@

Give $S$ the set of points in the space image. The segments could 
be built between wherever two points of $S$. However, to fulfill
 the cords with segments, only the points placed together could define
 a segment. To choose the correct points of $S$ a Delaunay triangulation
 is made over $S$ \cite{CGAL}. Each point of $S$ is a vertice 
of a triangle and then each potential segment is a side of a triangle. 
The Delaunay triangulations guarantee a unique solution with minimal
 internal angles for each triangle, which means  minimal length sides to the triangles \cite{GEOMETRICAL}.
 Give $\beta$ the cord surrounding the external hull of the Delaunay
 triangulation of $S$. An alpha shape algorithm uses a $\alpha \in N$ parameter,
 or square radius of a test circle, to travel from outside $\beta$ to inside
 the triangulation. The circle has to go through the triangles sides without touch the vertices. Give 
$n$ the number of triangles sides of triangulation
and $l_{i}$ with $i\in\{1,n\}$ the length of each side, if $\sqrt{\alpha} > l_{i}$ 
with $i \in\{1,n\}$, a segment is build between the respective vertices or
 points. At the end of the process, a  set of segments knows as $\alpha$-shape has been created.
  Note if $\sqrt{\alpha} > l_{i} \forall i$, the circle can’t be go inside $\beta$, then $\alpha$-shape
 is $\beta$ \cite{CGAL}. If $\sqrt{\alpha} < l_{i} \forall i$ the circle go through
 every side in the triangulation,  then no segment is created and $\alpha$-shape
 became $S$. The points that compound the droplet section are all contact neighbors. Then $\alpha = 1$
 is sufficient to create a segment set around the droplet
 (see figure \ref{photo-droplet-alpha-shape}).

\begin{figure}[h!]
\begin{center}    
\subfigure[t = ]{\label{photo-droplet-canny}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-droplet-canny.png}}
\subfigure[t = ]{\label{photo-droplet-alpha-shape}\includegraphics[width=3.5cm,height=3.5cm]{images/photo-droplet-alpha-shape.png}}\\
\end{center}
\caption{{\small Images series of macro drop profiles}}
\label{photo-results-droplet}
\end{figure}

@@

Now it is possible to determine the geometrical parameters shown 
at figure \ref{schema-macro-drop-droplet-parameters}. To compute the wetting 
angle measures, linear regressions or least squares (parabolic, ellipse, circle) 
are taken from the processed macro drop extracted profiles.
A loop algorithm applies this method to all frames at the experience to compute the wetting 
angles. Same procedure is used to estimate the macro drop radius and volume \cite{CHAPUIS}.

The metal transfert droplet is approximate and close with a combination of $\alpha$-shape and
graph algorithm. Once the set of segments are extracted a triangulation is created. The triangles 
are then used to compute the surface and the position of the centroid. It is assumed that there is a kind
of axisymmetry  and an homogeneous density in the droplet. With the triangles, the principal axis could also be 
computed.

\section{ Results}
In this part some results, performance and reliability of the library for a set of experiment
are shown. The basic experiment is a static PGMAW.
A macrodrop is feed by droplets that are assumed to flight vertically and
then feed the macrodrop. The macrodrop grows with a geometry that depends on the effects of gravity,
surface tension, heat transfert,...

To improve weld pool stability in pulsed GMAW, the growth of the droplet is investigated.
To improve weld quality, the transfert during some pulses are analyzed.

@@

\begin{itemize}
\item The speed of growth of the macro drop radius
\item The angle between the substrate and the liquid
\end{itemize}

The first is an indicator of the ease of growth of the macrodrop due to
heat transfert and tension surface and the second  item gives information
 on the capillarity mechanism involved in the macrodrop

The shielding gas has a great effect between the liquid and the gas interface. Gas could diffuse in the
first layer of the liquid and greatly modify the physical properties. The tension surface is the main physical
property that will be modified. A difference of tension surface will modify the shape of the interface by modifying
its equilibrium.
% It has to be kept in mind that modification of shielding composition will also modify
% the plasma energetical and momentum distribution that could also  influence the shape of the interface.

 To study the influence of the gases on the shape of the gas liquid interface, images must be selected in cold
regime of the plasma in the pulse. It is better to select images at the end of the period when the macrodrop is
stabilized. Once the images are selected, the algorithm described in section \ref{image_treatment} is used.
The treatment of each image lasts around 5ms.
\subsubsection{Basis and angle evolution} 
Some profile detection are shown on figure \ref{fig::photo-results-macro-drop} on the macrodrop.
The shape is shown on figure \ref{fig::photo-results-macro-drop}.

 The developped algorithm manage to detect profile under the arc.
 To isolate only 
macrodrop profile, a thershold relative to the base material is used to extract the macrodrop profile.
The result is shown on figure \ref{fig:profile_extract}. Then, basis and angle of the profile can be computed
all along  the process.
\begin{figure}[h!]
\centering    
\includegraphics[width=10cm]{images/CO2_2s.png}
\caption{Profile of macro drop for G1 gas after 2s of welding}
\label{fig::profile_extract}
\end{figure}
First, the evolution of the basis is extracted on figure \ref{fig::basis} by finding 
the min of the max of the contour on figure \ref{fig::profile_extract}.

@@

Another important geometrical entity is the angle of the macrodrop surface on the substrate.
 To approximate it, a simple linear regression is
performed for the first and last points of the profile. The result are shown on figure \ref{fig::angles}
for the left angle and the two gases.
\begin{figure}[h!]
\centering    
\includegraphics[width=7cm,angle=90]{images/Evolution_Angle_Gazs.pdf}
\caption{Macrodrop left Angle in function of welding time}
\label{fig::angles}
\end{figure}

The evolution curves are noisy. Videos investigation show that the macrodrop oscillates during welding. 
Macrodrop oscillations induced  wetting angle oscillations. Depending of the main oscillations during
a period, the local angle oscillation is more or less important. For pure Argon
gas, the equilibrium angle (60 degrees) rapidly reached and stays constant all along the welding.
For the 8 per cent $CO_2$ gas, the angle increase until reaching a constant value of 60 degrees.

\subsubsection{Discussion}
The noise in the measure for the basis could be attributed
to oscillations of the macrodrop coupled to the threshold for the detection of the macrodrop.

The interface between the gas and liquid is extremely strained. During a pulse, the surface is perturbated by the
increase of pressure in the arc due to increase of current and by the impingement of the droplet inside the
weld pool. These perturbations create oscillations of the macrodrop and on the free surface.
 These phenomenon induce also oscillations near the triple joint.

 The growth of the macrodrop is a balance mainly between
the energy balance (thermo convection) and the mechanical equilibrium (Dupr\'e's law and membrane equilibrium). 
The shape of the macrodrop is an important information for
the local and global equilibrium of the interface. 
For example, the macrodrop made with  pure Argon grows by step denoting an interesting instability 
of the interface.

The modification of gas influences surface tension but also modifies the energy transfert from the plasma
to the workpiece. Even with same welding parameters, 
the difference of gas will modify the current lines distribution but also the arc length.
Nevertheless, the evolution of the basis and the  shape 
(figure \ref{fig::comp_gazs}) for the two gases are almost the same (figure \ref{fig::macrodrop}).
 This means that at first order the two evolutions
are governed with the same mechanism (mass balance) and then the difference is due to heat transfert and surface tension.
Pure Argon shielding lead to a higher desequilibrium at the interface leading to a higher surface tension. Then the angle
at the triple joint (liquid-gas-substrate) is higher modifying then the behaviour of the overall interface.

@@

\subsection{ Droplet flight}
Droplet flight investigation is of interest for weld quality and the metal deposition process.
The determination of the motion and the impact point is then a good indicator of the quality of the
process. The droplet flight is only investigated for the 8 per cent $CO_2$ for a pulse of 113 Hertz.
The treatment of each image takes between 5 to 45ms with geometrical algorithm (triangulation) and output
(surface computation and position of the center of mass), within the python interpreter.

@@

The position of the center of mass of the droplet relative to the vertical axis shows that the 
droplet has a constant speed. The speed is estimated between 150mm/s to 200mm/s depending on the pulse
and the free flight of the droplet last 6ms.
